### 2019-06-03 01_introduction.tex
update

\tase{
The current archival version is an extension of previous work and several additions have been made to the draft to provide a more holistic inspection of the problem, chiefly:
\begin{enumerate}
	\item An additional benchmark has been added to demonstrate the efficacy of the proposed approach in problem domains where all the object positions do not lie in the shared workspace.
	\item It has been argued that smoothing can be used to alleviate the sychronization assumption. Data from the effects of smoothing the solutions in the experiments have been reported and show that the minor improvements highlight that in practice the synchronization assumption is not tragic.
	\item A k-arm extension of the asymptotic cost bound in the asynchronous case has been included.
	\item The proof for the asymptotic cost bound estimate for 2-arms under the synchronization assumption has been expanded, and Monte-Carlo trials have been reported in a simplified setup to validate the analysis model.
\end{enumerate}
}
%The computational costs of both the optimal
%and the proposed method are significantly improved from the lazy
%evaluation strategy. 
% When the synchronous solutions are smoothed to
% asynchronous ones, there is not significance difference in overall
% path quality. \kiril{This statement is unclear. What is the benefit from performing this step?}

>>>>

\tase{
The current archival version is an extension of previous work and several additions have been made to the draft to provide a more holistic inspection of the problem, chiefly:
\begin{enumerate}
	\item An additional benchmark has been added to demonstrate the efficacy of the proposed approach in problem domains where all the object positions do not lie in the shared workspace.
	\item It has been argued that smoothing can be used to alleviate the sychronization assumption. Data from the effects of smoothing the solutions in the experiments have been reported and show that the minor improvements highlight that in practice the synchronization assumption does not adversely affect solution quality to a great extent.
	\item A k-arm extension of the asymptotic cost bound in the asynchronous case has been included.
	\item The proof for the asymptotic cost bound estimate for 2-arms under the synchronization assumption has been expanded, and Monte-Carlo trials have been reported in a simplified setup to validate the analysis model.
\end{enumerate}
}
%The computational costs of both the optimal
%and the proposed method are significantly improved from the lazy
%evaluation strategy. 
% When the synchronous solutions are smoothed to
% asynchronous ones, there is not significance difference in overall
% path quality. \kiril{This statement is unclear. What is the benefit from performing this step?}

### 2019-06-03 08_evaluation.tex
update

\subsection{Discrete Reachability Benchmark}
In this benchmark, two Kuka arms are placed opposite a target arrangement table. The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image. The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms. This is indeed a simpler problem for the coordinated methods, but proves challenging to the naive random split strategy.

>>>>

\subsection{Discrete Reachability Benchmark}
In this benchmark, two Kuka arms are placed opposite a target arrangement table, as shown in Fig \ref{fig:reachability_benchmark}. The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image. The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms. This is indeed a simpler problem for the coordinated methods, but proves challenging to the naive random split strategy.
